### 2015-02-11 Docs/architecture/architecture.tex
remove the test suite docs -- this is now in BoxLib User's Guide
update location of the Fortran postprocessing tools

Finally the {\tt AmrPostprocessing} package provides simple
Fortran-based analysis routines (e.g.\ extract a line from a
multidimensional dataset) that operate on BoxLib datasets.  These are
described in \S~\ref{sec:analysis}.  Several sub-directories with
python-based routines are also here.  These are described both in
\S~\ref{sec:analysis} and \S~\ref{sec:vis:python}.

@@

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  After the projection, it is $\nabla \phi$ that modifies
the velocity field.  At a wall or for inflow conditions, we already
have the velocity we want at the boundary, so we want the velocity to
remain unchanged after the projection.  This requires $d\phi/dn=0$ on
those boundaries.  For outflow, we impose a condition that we do not
want the boundaries to introduce any tangental acceleration (or
shear), this is equivalent to setting $\phi = 0$ (then $\partial
\phi/d\partial t = 0$, with $t$ meaning `tangental').  This allows the
velocity to adjust as needed to the domain (see, for example,
\cite{almgrenBellSzymczak:1996}).

@@

>>>>

Finally the {\tt BoxLib/Tools/Postprocessing/F\_Src} package provides simple
Fortran-based analysis routines (e.g.\ extract a line from a
multidimensional dataset) that operate on BoxLib datasets.  These are
described in \S~\ref{sec:analysis}.  Several sub-directories with
python-based routines are also here.  These are described both in
\S~\ref{sec:analysis} and \S~\ref{sec:vis:python}.

@@

{\tt ell\_bc\_level\_array} is the analog to {\tt
  adv\_bc\_level\_array} for the elliptic solves in \maestro.  This
will come into play in the multigrid portions of the code.  The
actions that are used for {\tt ell\_bc\_level\_array} are either
Dirichlet or Neumann boundary condtions.  For the velocity
projections, we are dealing with a pressure-like quantity, $\phi$, so
the pressure boundary conditions here reflect the behavior we want for
the velocity.  After the projection, it is $\nabla \phi$ that modifies
the velocity field.  At a wall or for inflow conditions, we already
have the velocity we want at the boundary, so we want the velocity to
remain unchanged after the projection.  This requires $d\phi/dn=0$ on
those boundaries.  For outflow, we impose a condition that we do not
want the boundaries to introduce any tangental acceleration (or
shear), this is equivalent to setting $\phi = 0$ (then $\partial
\phi/\partial t = 0$, with $t$ meaning `tangental').  This allows the
velocity to adjust as needed to the domain (see, for example,
\cite{almgrenBellSzymczak:1996}).

@@

\section{Regression Testing}

There is an extensive regression test suite for \boxlib\ that works with
\maestro.  Full details, and a sample \maestro\ configuration file are
provided in the \boxlib\ User's Guide and source.
